\textbf{Selective DNA and Protein Isolation from Marine Macrophyte Surfaces}

### 2020-11-21 submission/manuscript.Rmd
Text formatting.

\newpage
```{r out.width="100%", fig.align="center", fig.cap="Taxonomic classification and relative contribution of the most abundant ($\\geq$1 \\si{\\percent}) bacterial and archaeal sequences from surfaces of two marine macrophytes (\\textit{C. nodosa} and \\textit{C. cylindracea}) sampled in the Bay of Saline and the Bay of Funtana (mixed and monospecific settlements) and in two contrasting seasons (4 December 2017 and 19 June 2018).\\label{community}", fig.pos="ht"}
include_graphics("../results/figures/community_bar_plot.jpg")
```

>>>>

\newpage
```{r out.width="100%", fig.align="center", fig.cap="Taxonomic classification and relative contribution of the most abundant ($\\geq$ 1 \\si{\\percent}) bacterial and archaeal sequences from surfaces of two marine macrophytes (\\textit{C. nodosa} and \\textit{C. cylindracea}) sampled in the Bay of Saline and the Bay of Funtana (mixed and monospecific settlements) and in two contrasting seasons (4 December 2017 and 19 June 2018).\\label{community}", fig.pos="ht"}
include_graphics("../results/figures/community_bar_plot.jpg")
```

### 2020-11-21 submission/manuscript.tex
Text formatting.

\caption{Taxonomic classification and relative contribution of the most abundant ($\geq$1 \si{\percent}) bacterial and archaeal sequences from surfaces of two marine macrophytes (\textit{C. nodosa} and \textit{C. cylindracea}) sampled in the Bay of Saline and the Bay of Funtana (mixed and monospecific settlements) and in two contrasting seasons (4 December 2017 and 19 June 2018).\label{community}}\label{fig:unnamed-chunk-3}
\end{figure}

>>>>

\caption{Taxonomic classification and relative contribution of the most abundant ($\geq$ 1 \si{\percent}) bacterial and archaeal sequences from surfaces of two marine macrophytes (\textit{C. nodosa} and \textit{C. cylindracea}) sampled in the Bay of Saline and the Bay of Funtana (mixed and monospecific settlements) and in two contrasting seasons (4 December 2017 and 19 June 2018).\label{community}}\label{fig:unnamed-chunk-3}
\end{figure}
